### 2012-11-28 inst/examples/reed-example.Rmd
functionalized methods into R/
Different GP fitting routines can all be called with gp_fit and plotted with plot.gpfit.

transition matrices for GP can be estimated with gp_transition_matrices.

See example use in reed-example.R

```{r graphing-options, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(ggplot2)
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA)
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

```{r results="hide"}
knit("beverton_holt_data.Rmd")
```

@@

```{r}
library(nonparametricbayes)
gp <- gp_fit(obs, X, c(sigma_n=1, l=1.5))
plot.gpfit(gp)
```

Solution using `kernlab`

```{r}
library(kernlab)
#gp <- gausspr(obs$x, obs$y, kernel="rbfdot", kpar=list(sigma=0.5), fit=FALSE, scaled=FALSE, var=.09)
gp <- gausspr(obs$x, obs$y, kernel="rbfdot", scaled=FALSE, var=sigma_g^2)
Ef <- predict(gp, X)
```

Manually get the covariance, $K(x_*, x_*) - K(x_*, x)(K(x, x) - \sigma_n^2\mathbb{I})^{-1}K(x,x_*)$.

```{r}
var <- gp@kcall$var
var <- 9
Inv <- solve(kernelMatrix(kernelf(gp), xmatrix(gp)) + diag(rep(var, length = length(xmatrix(gp)))))
Cf <- kernelMatrix(kernelf(gp), as.matrix(X)) - 
  kernelMult(kernelf(gp), as.matrix(X), xmatrix(gp),  Inv) %*% 
  kernelMatrix(kernelf(gp), xmatrix(gp), as.matrix(X))
```

```{r}
require(ggplot2)
dat <- data.frame(x=X, y=(Ef), ymin=(Ef-2*sqrt(diag(Cf))), ymax=(Ef+2*sqrt(diag(Cf))))    
ggplot(dat) + 
  geom_ribbon(aes(x=x,y=y, ymin=ymin, ymax=ymax), fill="grey80") +
  geom_line(aes(x=x,y=y), size=1) +
  geom_point(data=obs,aes(x=x,y=y)) + 
  scale_y_continuous(name="output, f(x)") + xlab("input, x") 
```

@@

```{r}
rownorm <- function(M) t(apply(M, 1, function(x) x/sum(x)))
h_grid <- x_grid
```

Define a transition matrix $F$ from the Gaussian process, giving the probability of going from state $x_t$ to $x_{t+1}$.
We already have the Gaussian process mean and variance predicted for each point $x$ on our grid, so this is simply:

```{r}
V <- sqrt(diag(Cf))
matrices_gp <- lapply(h_grid, function(h){
  F <- sapply(x_grid, function(x) dnorm(x, Ef-h, V))
  F <- rownorm(F)
})
```

True $f(x)$

```{r}
matrices_true <- lapply(h_grid, function(h){
  mu <- sapply(x_grid, f, h, p)
  F_true <- sapply(x_grid, function(x) dnorm(x, mu, sigma_g))
  F_true <- rownorm(F_true)
})
```

Calculate the policy function using the true F:

```{r}
opt_true <- find_dp_optim(matrices_true, x_grid, h_grid, 20, 0, profit, delta=.01)
```

Calculate using the inferred GP

```{r}
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```

>>>>

```{r graphing-options, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(ggplot2)
library(kernlab)
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE)
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

```{r results="hide"}
knit("beverton_holt_data.Rmd")
true <- data.frame(x = X, y = sapply(X, f, 0, p))
```

@@

```{r}
gp <- gp_fit(obs, X, c(sigma_n=.2, l=10))
plot.gpfit(gp, true)
```

@@

```{r}
matrices_gp <- gp_transition_matrix(gp)
matrices_true <- f_transition_matrix(f, p, x_grid)
opt_true <- find_dp_optim(matrices_true, x_grid, h_grid, 20, 0, profit, delta=.01)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```
